Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-10 paper.tex
Added styling to Shabby references throughout

To train our model, we developed the ShabbyPages dataset \cite{ref_ShabbyPages}, a real-world document image corpus with \emph{Augraphy}-generated synthetic noise.
Gathering the 600 ground-truth documents was the most challenging part, requiring the efforts of several workers across multiple days. Adding the noise to these images was trivial however; \emph{Augraphy} makes it easy to produce large training sets.
For additional realistic variation, we also gathered 300 paper textures and used the PaperFactory augmentation to ``print'' our source documents onto these.

@@

Another new dataset --- ShabbyReal --- was produced as part of the larger ShabbyPages corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.  ShabbyReal is fully out-of-distribution for the models in our experiments, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.

@@

\begin{table}
\centering
\caption{Model training statistics and performance on ShabbyReal validation task}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Metric & PSNR & SSIM & RMSE\\
\hline
Augraphy\_UNet & 63.35 & 0.87 & 0.18\\
Augraphy\_NAFNet & & &
Augraphy\_NAFNet_large & & &
\hline
\end{tabular}
\end{table}

@@

We first compiled 15 ground-truth, noise-free document images from a new corpus of born-digital documents, whose ground-truth strings are known. We then used Tesseract to generate OCR predictions on these noise-free documents, as a baseline for comparison. We considered these OCR predictions as the ground-truth labels for each document. Next, we generated noisy versions of the 15 documents by running them through an \emph{Augraphy} pipeline, and again used Tesseract to generate OCR predictions on these noisy documents. We compared the word accuracy rate on the noisy OCR results versus the ground-truth noise-free OCR results, and found that the noisy OCR results were on average 52\% less accurate, with a range of up to 84\%. This example use-case demonstrates the effectiveness of using \emph{Augraphy} to create challenging test data for evaluating OCR systems.

>>>>

To train our model, we developed the \emph{ShabbyPages} dataset \cite{ref_ShabbyPages}, a real-world document image corpus with \emph{Augraphy}-generated synthetic noise.
Gathering the 600 ground-truth documents was the most challenging part, requiring the efforts of several crowdworkers across multiple days. Adding the noise to these images was trivial however; \emph{Augraphy} makes it easy to produce large training sets.
For additional realistic variation, we also gathered 300 paper textures and used the PaperFactory augmentation to ``print'' our source documents onto these.

@@

Another new dataset --- \emph{ShabbyReal} --- was produced as part of the larger \emph{ShabbyPages} corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.  \emph{ShabbyReal} is fully out-of-distribution for the models in our experiments, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.

@@

\begin{table}
\centering
\caption{Model training statistics and performance on \emph{ShabbyReal} validation task}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Metric & PSNR & SSIM & RMSE\\
\hline
Augraphy\_UNet & 63.35 & 0.87 & 0.18\\
Augraphy\_NAFNet & & &
Augraphy\_NAFNet_large & & &
\hline
\end{tabular}
\end{table}

@@

We first compiled 15 ground-truth, noise-free document images from a new corpus of born-digital documents, whose ground-truth strings are known. We then used Tesseract to generate OCR predictions on these noise-free documents, as a baseline for comparison. We considered these OCR predictions as the ground-truth labels for each document. Next, we generated noisy versions of the 15 documents by running them through an \emph{Augraphy} pipeline, and again used Tesseract to generate OCR predictions on these noisy documents. We compared the word accuracy rate on the noisy OCR results versus the ground-truth noise-free OCR results, and found that the noisy OCR results were on average 52\% less accurate, with a range of up to 84\%. This example use-case demonstrates the effectiveness of using \emph{Augraphy} to create challenging test data that remains human readable suitable for evaluating OCR systems.
